Appendix

### 2020-05-17 appendixupdates/appendixV3.Rmd
Original contents of appendixupdates
Version: 2020-05-14

---
title: "Appendix"
author: "Umberto Mignozzetti"
date: "12/25/2019"
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}

output: pdf_document
---

```{=latex}
\tableofcontents
```

@@

```{r global_options, include=FALSE}
## Starting
set.seed(732578) # From random.org

# Needed packages
pkgs <- c('tidyverse', 'meta', 'metafor', 'readxl',
          'knitr', 'gridGraphics', 'gridExtra','ggpubr','kableExtra','magick')

# Install if not already installed
installIfNot <- function(x) {
  if(x %in% rownames(installed.packages()) == FALSE) 
    install.packages(x, dependencies = T, repos = "http://cran.us.r-project.org")
} 
lapply(pkgs, installIfNot)

@@

# Knitr options
knitr::opts_chunk$set(fig.pos = 'H') # holds figure position

```

```{r, echo=FALSE, include=FALSE}

@@

dat <- dat[order(dat$id),]
dat <- dat[!is.na(dat$coef),]
row.names(dat) <- NULL
levels(dat$elecsys2) <- c('Majoritarian', 'Non-Majoritarian')
dat$scoef <- factor(as.character(dat$scoef), labels = c('N', 'P'))
dat$scoefsig <- factor(as.character(dat$scoefsig), labels = c('N', 'P'))
levels(dat$scoef) <- c('Negative', 'Positive')
levels(dat$scoefsig) <- c('Negative', 'Positive')
dat$method <- factor(as.character(dat$method), 
                     levels = c("OLS", "PANEL", "IV", "RDD"))
dat$location2 <- as.character(dat$location)
dat$location2[dat$location2!='World'] = 'Country'
dat$location2 <- factor(as.character(dat$location2), 
                     levels = c("Country", "World"))
dat$agglevel <- factor(as.character(dat$agglevel), 
                     levels = c("Local", "States", "Countries"))
fulldat <- dat
dat <- dat %>%
  filter(usemeta == 1)
```
\newpage
## Descriptive statistics

@@

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Study Year Frequencies"}
dat %>%
  ggplot(aes(x = as.factor(year))) + 
    geom_bar(color = "black") + 
  labs(x = "",
       y = "") + 
  theme_bw()
```

\newpage
### Published?

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
dat %>%
  ggplot(aes(x = as.factor(published))) + 
    geom_bar(color = "black") + 
  labs(x = "Published study?",
       y = "") + 
  theme_bw()

```

\newpage
### Dependent variables

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
dat %>%
  mutate(depvar2 = factor(depvar2, 
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") + 
  labs(x = "Dependent Variables",
       y = "") + 
  coord_flip() + 
  theme_bw()

```

\newpage
### Independent variables

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Independent variables across the law of 1/n studies"}
dat %>%
  mutate(indepvar2 = factor(indepvar2, labels = c('K (upper house legislators)',
                                                  'N (lower house legislators)',
                                                  'Log N'))) %>%
  ggplot(aes(x = indepvar2)) + 
    geom_bar(color = "black") + 
  labs(x = "Independent Variables",
       y = "") +
  coord_flip() +
  theme_bw() 
```

\newpage
### Histogram Coefficients

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Coefficients"}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") + 
  labs(x = "Coefficients") + 
  theme_bw()

```

\newpage
### Histogram Standard Errors

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Standard Errors"}
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") + 
  labs(x = "Standard Errors") + 
  theme_bw()

```

\newpage
### Sign Coefficients

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign?"}
dat %>%
  ggplot(aes(x=as.factor(scoef))) + 
  geom_bar(color = "black") + 
  labs(x = "Coefficient Sign",
       y = "") +
  theme_bw()
```

@@

```{r, echo=FALSE}
aux <- filter(dat, indepvar2 == 'N')
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```

@@

```{r, echo=FALSE}
aux <- filter(dat, indepvar2 == 'K')
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```

@@

\newpage
### Electoral system

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Electoral system"}
dat %>%
  ggplot(aes(x=as.factor(elecsys2))) + 
    geom_bar(color = "black") + 
  labs(x = "Electoral system",
       y = "") + 
  theme_bw()
```

\newpage
### Electoral system x Sign Coefficient

@@

\newpage
### Independent Variable x Sign Coefficient

@@

\newpage
### Dependent variables x Independent variables

@@

\newpage 
### Descriptive Stats of Moderators

```{r, echo=F,warning=F,message=F,error=F}

# Table 2

dat2 <- dat %>%
  select(depvar2, indepvar2, published, elecsys2, method,agglevel, location2) %>%
  rename(Depvar = depvar2,
         Indepvar = indepvar2,
         Published = published,
         "Electoral System" = elecsys2,
         Method = method,
         "Aggregate Level" = agglevel,
         Location = location2)

names <- dat2 %>% 
  map(table) %>%
  unlist() %>%
  names()

aux <- dat2 %>%
  map_df(~{
    table(.x) %>%
      as.data.frame() %>%
      rename(Moderator = ".x") %>%
      mutate(Moderator = as.character(Moderator),
             Pct = paste0(100*(round(Freq/sum(Freq, na.rm = T), digits = 4)), "%"))
  }) %>%
  mutate(Moderator = names,
         Moderator = gsub("\\.", ": ", Moderator),
         Freq = as.character(Freq)) %>%
  bind_rows(.,
            tibble(
              Moderator = "Year",
              Freq = paste0(round(mean(dat$year, na.rm = T), digits=2), " (Mean)"),
              Pct = paste0(as.character(round(median(dat$year, na.rm = T), digits=2)), " (Median)")
            ))

kable(aux,
      booktabs = T,
      align = "c",
      linesep ='') %>% 
  kable_styling(c("striped","bordered","scale_down"), position = "center")

rm(dat2,names)
```

\newpage
## Meta-analysis

We combined the three independent variables (N, logN, and K) with the levels of the three dependent variables (ExpPC, logExpPC, PCTGDP). This formed a 3x3 possibility for our analysis.

@@

```{r, echo=FALSE}
# Pooling effects analysis -- ExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f1 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1)) 
f1
```

```{r,include=F,warning=F}
f1 + 
  labs(caption = "ExpPC x N") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/fa.png", width = 30, height = 18.75, units = "cm")

```

@@

\newpage
#### Electoral system subgroup analysis

@@

```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)

mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f1b <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f1b
```

@@

\newpage
### ExpPC x logN

\newpage
### ExpPC x K

```{r}
# Pooling effects analysis -- ExpPC x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

@@

```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f2 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f2
```

```{r,include=F,warning=F}
f2 + 
  labs(caption = "ExpPC x K") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/fb.png", width = 30, height = 18.75, units = "cm")

```

@@

\newpage
### logExpPC x N

@@

```{r}
# Pooling effects analysis -- logExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

mod <- metagen(
  coef, SE, data=aux, 
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction = TRUE,
  sm="SMD"
  )

mod
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f3 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f3
```

```{r,include=F,warning=F}
f3 + 
  labs(caption = "logExpPC x N") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/fc.png", width = 30, height = 18.75, units = "cm")

```

@@

\newpage
### logExpPC x logN

@@

```{r}
# Pooling effects analysis -- logExpPC x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f4 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f4
```

```{r,include=F,warning=F}
f4 + 
  labs(caption = "logExpPC x logN") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/fd.png", width = 30, height = 18.75, units = "cm")

```

@@

\newpage
### logExpPC x K

```{r}
# Pooling effects analysis -- PCTGDP x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f5 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1)) 
f5
```

```{r,include=F,warning=F}
f5 + 
  labs(caption = "PCTGDP x N") +
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 18, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1),
        plot.caption = element_text(size=22))

ggsave("./plots/fe.png", width = 30, height = 18.75, units = "cm")

```

\newpage
### PCTGDP x logN

```{r}
# Pooling effects analysis -- PCTGDP x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

mod <- metagen(
  coef, SE, data=aux, 
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction=TRUE,
  sm="SMD"
  )

mod
```

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f6 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) + 
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f6
```

>>>>

---
title: "Appendix"
author: "Umberto Mignozzetti"
date: "12/25/2019"
output: pdf_document
---

@@

```{r, echo=FALSE, include=FALSE}
## Starting
set.seed(732578) # From random.org

# Needed packages
pkgs <- c('tidyverse', 'meta', 'metafor', 
          'readxl', 'dmetar')

# Install if not already installed
installIfNot <- function(x) {
  if(x %in% rownames(installed.packages()) == FALSE) 
    install.packages(x, dependencies = T)
} 
lapply(pkgs, installIfNot)

@@

@@

dat <- dat[order(dat$id),]
dat <- dat[!is.na(dat$coef),]
row.names(dat) <- NULL
levels(dat$elecsys2) <- c('Majoritarian', 'Non-Majoritarian')
dat$scoef <- factor(as.character(dat$scoef), labels = c('N', 'P'))
dat$scoefsig <- factor(as.character(dat$scoefsig), labels = c('N', 'P'))
levels(dat$scoef) <- c('Negative', 'Positive')
levels(dat$scoefsig) <- c('Negative', 'Positive')
dat$method <- factor(as.character(dat$method), 
                     levels = c("OLS", "PANEL", "IV", "RDD"))
dat$location2 <- as.character(dat$location)
dat$location2[dat$location2!='World'] = 'Country'
dat$location2 <- factor(as.character(dat$location2), 
                     levels = c("Country", "World"))
dat$agglevel <- factor(as.character(dat$agglevel), 
                     levels = c("Local", "States", "Countries"))
fulldat <- dat
dat <- dat %>%
  filter(usemeta==1)
```

## Descriptive statistics

@@

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Study Year Frequencies"}
ggplot(dat, aes(x=as.factor(year))) + 
  geom_bar() + xlab('') + theme_bw() +
  ylab('')
```

### Published?

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
ggplot(dat, aes(x=as.factor(published))) + 
  geom_bar() + xlab('Published study?') + theme_bw() +
  ylab('')
```

### Dependent variables

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
ggplot(dat, aes(x=factor(dat$depvar2, labels = c('Per Capita Expenditure', 'Percentage GDP Government Expenditure','Log Per Capita Expenditure')))) + 
  geom_bar() + xlab('Dependent Variables') + theme_bw() +
  ylab('') + coord_flip()
```

### Independent variables

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Independent variables across the law of 1/n studies"}
ggplot(dat, aes(x=factor(dat$indepvar2, labels = c('K (upper house legislators)', 'N (lower house legislators)','Log N')))) + 
  geom_bar() + xlab('Independent Variables') + theme_bw() +
  ylab('') + coord_flip()
```

### Histogram Coefficients

```{r, echo=FALSE}
hist(dat$coef, main = '', xlab = 'Coefficients')
```

### Histogram Standard Errors

```{r, echo=FALSE}
hist(dat$SE, main = '', xlab = 'Standard Errors')
```

### Sign Coefficients

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign?"}
ggplot(dat, aes(x=as.factor(scoef))) + 
  geom_bar() + xlab('Coefficient Sign') + theme_bw() +
  ylab('')
```

@@

```{r, echo=FALSE}
aux <- filter(dat, indepvar2=='N')
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```

@@

```{r, echo=FALSE}
aux <- filter(dat, indepvar2=='K')
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```

@@

### Electoral system

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Electoral system"}
ggplot(dat, aes(x=as.factor(elecsys2))) + 
  geom_bar() + xlab('Electoral system') + theme_bw() +
  ylab('')
```

### Electoral system x Sign Coefficient

@@

### Independent Variable x Sign Coefficient

@@

### Dependent variables x Independent variables

@@

## Meta-analysis

We combined the three independent (N, logN, and K) with the levels of the three dependent variables (ExpPC, logExpPC, PCTGDP). This formed a 3x3 possibility for our analysis.

@@

```{r, echo=FALSE}
# Pooling effects analysis -- ExpPC x N
aux <- filter(dat,
              indepvar2=='N'&depvar2=='ExpPC')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE)
```

@@

#### Electoral system subgroup analysis

@@

```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system"}
mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3,
       test.subgroup.random = TRUE)
```

@@

```{r}
# Pooling effects analysis -- PCTGDP x N
aux <- filter(dat,
              indepvar2=='N'&depvar2=='PCTGDP')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE)
```

@@

### logExpPC x N

@@

```{r}
# Pooling effects analysis -- logExpPC x N
aux <- filter(dat,
              indepvar2=='N'&depvar2=='logExpPC')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
```

@@

### ExpPC x logN

```{r}
# Pooling effects analysis -- PCTGDP x logN
aux <- filter(dat,
              indepvar2=='logN'&depvar2=='PCTGDP')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
```

### logExpPC x logN

@@

```{r}
# Pooling effects analysis -- logExpPC x logN
aux <- filter(dat,
              indepvar2=='logN'&depvar2=='logExpPC')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
```

@@

### ExpPC x K

```{r}
# Pooling effects analysis -- ExpPC x K
aux <- filter(dat,
              indepvar2=='K'&depvar2=='ExpPC')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

@@

```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
```
